\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-30 paper.qmd
Aggregate notations
tidying of table and summary paragraph

@@

```{r}
# Notations used in the paper

notation_df <- read_csv("data/paper_notations.csv")

# Create the table
kable(notation_df, format = "latex", booktabs = TRUE, escape = FALSE, 
      caption = "Notations used in this paper.", label = "tbl-notations") |>
  kable_styling(latex_options = c("HOLD_position"), position = "center", full_width = FALSE, font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:2, width = c("5cm", "12cm"))
```

<< XXX Jayani, please insert a table of notation >>

>>>>

\spacingset{1.0} <!--% command in JASA style, comment to go back to double spacing-->

@@

@tbl-notation summarises the notation used to explain the new methodology.

```{r}
#| label: tbl-notation
#| tbl-cap: "Summary of notation for describing new methodology."
# Notations used in the paper

notation_df <- read_csv("misc/notation.csv")

# Create the table
kable(notation_df, 
      format = "latex", 
      booktabs = TRUE, escape = FALSE) |>
  kable_styling(latex_options = c("HOLD_position"),
                position = "center", 
                full_width = FALSE, 
                font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:2, width = c("5cm", "12cm"))
```

### 2024-03-30 paper.tex
tidying of table and summary paragraph

@@

\begin{table}[H]

\caption{\label{tab:tbl-notations}Notations used in this paper.}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n$ & number of observations\\
$p$ & number of variables in $p$-D data\\
$d$ & number of dimensions in embedding data, usually two\\
$X_{n \times p} = \begin{bmatrix} \textbf{x} _{1} & \textbf{x}_ {2} & \cdots & \textbf{x}_{n} \\  \end{bmatrix}^\top$ & $p$-D data matrix\\
$Y_{n \times d} = \begin{bmatrix} \textbf{y} _{1} & \textbf{y}_ {2} & \cdots & \textbf{y}_{n} \\  \end{bmatrix}^\top$ & embedding matrix\\
\addlinespace
$P_t$, $P_{t+1}$ & point along the geodesic path at time $t$ and the next time instant, which is $t+1$\\
$y_{max}$ & maximum value of the scaled second embedding component\\
$r_1$, $r_2$ & range of the first and  second embedding component\\
$h_b$, $w_b$ & height and width of the hexagon\\
$a_r$ & aspect ratio of the 2D layout before scaling\\
\addlinespace
$h_r$ & hexagon ratio\\
$s$ & hexagonal size (radius of the outer circle surrounding the hexagon)\\
$(x_s, y_s)$ & starting coordinates of the hexagonal grid\\
$q_x$, $q_y$ & buffer amount along the x and y axes\\
$h_s$, $v_s$ & horizontal and vertical distance between adjacent hexagon bin centroids\\
\addlinespace
$d_x$, $d_y$ & horizontal spacing and adjusted vertical spacing for hexagonal coordinates\\
$b_x$, $b_y$ & number of hexagon bins along the x and y axes\\
$b$, $b'$ & total and non-empty hexagon bins in the grid\\
$n_k$ & number of observations within $k^{th}$ hexagon\\
$(h^k_{x_i}, h^k_{y_i})$ & hexagonal grid coordinates of $k^{th}$ hexagon\\
\addlinespace
$C_k^{(2)} \equiv (C_{ky_1}, C_{ky_2})$ & hexagonal bin centroid coordinates of $k^{th}$ hexagon\\
$C_k^{(p)} \equiv (C_{kx_1}, ..., C_{kx_p})$ & $p$-D mappings of 2D hexagonal bin centroids of $k^{th}$ hexagon\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\spacingset{1.0}

@@

Table~\ref{tbl-notation} summarises the notation used to explain the new
methodology.

\begin{table}

[H]
\centering\begingroup\fontsize{12}{14}\selectfont

\begin{tabular}{>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{12cm}}
\toprule
\textbf{Notation} & \textbf{Description}\\
\midrule
$n, p, d$ & number of observations, variables, embedding dimension, respectively\\
$X_{n \times p} = \begin{bmatrix} \textbf{x} _{1} & \textbf{x}_ {2} & \cdots & \textbf{x}_{n} \\  \end{bmatrix}^\top$ & observed data matrix\\
$Y_{n \times d} = \begin{bmatrix} \textbf{y} _{1} & \textbf{y}_ {2} & \cdots & \textbf{y}_{n} \\  \end{bmatrix}^\top$ & reduced dimension, embedding matrix\\
$P_t$, $P_{t+1}$ & point along the geodesic path at time $t$ and the next time instant, which is $t+1$\\
$y_{max}$ & maximum value of the scaled second embedding component\\
\addlinespace
$r_1$, $r_2$ & range of the first and  second embedding component\\
$h_b$, $w_b$ & height and width of the hexagon\\
$a_r$ & aspect ratio of the 2D layout before scaling\\
$h_r$ & hexagon ratio\\
$s$ & hexagonal size (radius of the outer circle surrounding the hexagon)\\
\addlinespace
$(x_s, \ y_s)$ & starting coordinates of the hexagonal grid\\
$q_x$, $q_y$ & buffer amount along the x and y axes\\
$h_s$, $v_s$ & horizontal and vertical distance between adjacent hexagon bin centroids\\
$d_x$, $d_y$ & horizontal spacing and adjusted vertical spacing for hexagonal coordinates\\
$b_x$, $b_y$ & number of hexagon bins along the x and y axes\\
\addlinespace
$b$, $b'$ & total and non-empty hexagon bins in the grid\\
$n_k$ & number of observations within the $k^{th}$ hexagon\\
$(h^k_{x_i}, h^k_{y_i})$ & hexagonal grid coordinates of the $k^{th}$ hexagon\\
$C_k^{(2)} \equiv (C_{ky_1}, C_{ky_2})$ & hexagonal bin centroid coordinates of the $k^{th}$ hexagon\\
$C_k^{(p)} \equiv (C_{kx_1}, ..., C_{kx_p})$ & $p$-D mappings of 2D hexagonal bin centroids of the $k^{th}$ hexagon\\
\bottomrule
\end{tabular}
\endgroup{}

\caption{\label{tbl-notation}Summary of notation for describing new
methodology.}

\end{table}%
